### 2025-02-06 ESC195 Lecture Notes/main.tex
feb 6

\paragraph{Convergent Sequences} A sequence $\{a_n\}$ is said to be convergent if there exists a number $L$ such that for all $\epsilon > 0$, there exists an $N$ such that $|a_n - L| < \epsilon$ for all $n \ge N$.

>>>>

\begin{definition}[Unbounded Sequences]
    A sequence $\{a_n\}$ is said to be unbounded if it is not bounded above or below. We can prove it using a epsilon-delta proof or considering the derivatives of the function that defines the sequence.
    Proof that the sequence $\{a_n\} = 2^n$ is unbounded. Let $M$ be a number, we can find an $n$ such that $2^n > M$. We can find this $n$ by taking the logarithm of $M$ to the base $2$.
    Proof that the sequence $\{a_n\} = \frac{x^2}{e^x}$ is bounded above. We show that the derivative is negative after a certain point ($x = 2$), thus the sequence is bounded above.
\subsection{The Limit of a Sequence}
\begin{definition}[Limit of a Sequence]
    The limit of a sequence $\{a_n\}$ is given by:
        \lim_{n \to \infty} a_n = L
    if for every $\epsilon > 0$, there exists an $N$ such that $|a_n - L| < \epsilon$ for all $n > N$. We denote this as $a_n \to L$ as $n \to \infty$.
\paragraph{Convergence} A sequence $\{a_n\}$ is said to converge to $L$ if the limit of the sequence is $L$. And the following are true:
    \item If a sequence converges, then it is bounded.
    \item If a sequence is unbounded, then it does not converge, i.e. it diverges.
    \item However, if a sequence is bounded, it may or may not converge.
    Prove that the sequence $\{a_n\} = \frac{n}{n+1}$ converges to $1$. We can show that $|a_n - 1| < \epsilon$ for all $n > N$ by taking $N = \frac{1}{\epsilon}$ by some algebraic manipulation. We have:\\
    Given $\epsilon > 0$, let $N = \frac{1}{\epsilon}$, then for all $n > N$:
        |a_n - 1| &= |\frac{n}{n+1} - 1| \\
        &= |\frac{n - n - 1}{n+1}| \\
        &= \frac{1}{n+1} < \frac{1}{n} < \epsilon
\begin{theorem}[Uniqueness of Limits]
    The limit of a sequence is unique. That is, of $\lim_{n \to \infty} a_n = L$ and $\lim_{n \to \infty} a_n = M$, then necessarily $L = M$.
\begin{theorem}[Monotone Convergence Theorem]
    A monotonic sequence is convergent if and only if it is bounded. And necessarily the following are true if the sequence converges:
        \item If the sequence is increasing or non decreasing, then the limit is the supremum of the sequence.
        \item If the sequence is decreasing or non increasing, then the limit is the infimum of the sequence.
\begin{theorem}[Limit Operations]
    Given two sequences $\{a_n\}$ and $\{b_n\}$, and $c \in \mathbb{R}$, we have:
        \item \textbf{Sum of Limits}: $\lim_{n \to \infty} (a_n + b_n) = \lim_{n \to \infty} a_n + \lim_{n \to \infty} b_n$
        \item \textbf{Product of Limits}: $\lim_{n \to \infty} (a_n \cdot b_n) = \lim_{n \to \infty} a_n \cdot \lim_{n \to \infty} b_n$
        \item \textbf{Scalar Multiple of Limits}: $\lim_{n \to \infty} c \cdot a_n = c \cdot \lim_{n \to \infty} a_n$
        \item \textbf{reciprocal of Limits}: $\lim_{n \to \infty} \frac{1}{a_n} = \frac{1}{\lim_{n \to \infty} a_n}$
        \item \textbf{Quotient of Limits}: $\lim_{n \to \infty} \frac{a_n}{b_n} = \frac{\lim_{n \to \infty} a_n}{\lim_{n \to \infty} b_n}$, provided $\lim_{n \to \infty} b_n \neq 0$
\begin{theorem}[Squeeze Theorem\footnote{Also known as the Sandwich Theorem or the Pinching Theorem}]
    Given three sequences $\{a_n\}$, $\{b_n\}$, and $\{c_n\}$, if $a_n \le b_n \le c_n$ for all $n$, and $\lim_{n \to \infty} a_n = \lim_{n \to \infty} c_n = L$, then necessarily $\lim_{n \to \infty} b_n = L$. This is useful for proving limits of sequences.
\begin{theorem}[Composite Function]
    Given sequence $\{a_n\}$ covnerges to $L$ and continuous function $f$ at $L$, we have:
        \lim_{n \to \infty} f(a_n) = f(\lim_{n \to \infty} a_n)
\paragraph{Some Common Limits} Some common limits of sequences are:
    \item for $a > 0$, $\lim_{n \to \infty} a^{1/n} = 1$
    \item for $|a| < 1$, $\lim_{n \to \infty} a^n = 0$
    \item for $a > 0$, $\lim_{n \to \infty} \frac{1}{n^a} = 0$
    \item for $a > 0$, $\lim_{n \to \infty} \frac{a^n}{n!} = 0$
\subsection{Series}
\begin{definition}[Infinite Series]
    An infinite series is the sum of the terms of an infinite sequence. We denote the sum of the series as:
        S = \sum_{n=1}^{\infty} a_n = a_1 + a_2 + a_3 + \ldots
    We also denote it as just $\sum a_n$.
\begin{definition}[Partial Sum]
    The partial sum of an infinite series is the sum of the first $n$ terms of the series. We denote the partial sum as:
        S_n = \sum_{i=1}^{n} a_i = a_1 + a_2 + \ldots + a_n
    If the sequance $\{S_n\}$ converges to $S$, then the series is said to converge to $S$; otherwise, it is said to diverge.
\paragraph{Geometric Series} A geometric series is a series of the form:
    \sum_{n=0}^{\infty} ar^n = a + ar + ar^2 + \ldots
\begin{theorem}[Geometric Series]
    A geometric series converges if $|r| < 1$, and the sum of the series is given by:
        S = \frac{a}{1 - r}
    If $|r| \ge 1$, then the series diverges.
\begin{theorem}[Addition of Series]
    Given two series $\sum a_n$ and $\sum b_n$, we have:
        \sum a_n + \sum b_n = \sum (a_n + b_n)
\begin{theorem}[Convergence]
    $\sum a_n$ converges if and only if $\sum_{k=j}^{\infty} a_k$ converges for all $j$.
    Given $\sum \frac{3^{k-1}}{4^{3k+1}}$ converges. Then we have:
        \sum \frac{3^{k-1}}{4^{3k+1}} = \frac{1}{12} + \frac{1}{64} + \frac{1}{4^7} + \ldots_n + \sum^{\infty}_{k=n} \frac{3^{k-1}}{4^{3k+1}}
    converges for all $n$.
\begin{theorem}[Zero Test, Divergence Test]
    If $\lim_{n \to \infty} a_n \ne 0$, then $\sum a_n$ diverges. Note that the contrapositive is true, i.e. if $\sum a_n$ converges, then $\lim_{n \to \infty} a_n = 0$.
\subsection{The Integral Test and Estimates of Sums}
\begin{theorem}[Integral Test]
    Let $f$ be a continuous, positive, and decreasing function on $[1, \infty)$, and let $a_n = f(n)$. Then the series $\sum a_n$ converges if and only if the improper integral $\int_1^{\infty} f(x) \, dx$ converges.
\begin{example}[$p$=2-series]
    Given $\sum \frac{1}{n^2}$, we can use the integral test to show that the series converges. We have:
        \int_1^{\infty} \frac{1}{x^2} \, dx &= -\frac{1}{x} \Big|_1^{\infty} \\
        &= 1
    Thus, the series converges.
Note that the ``iff'' statement allow us to determine the convergence of an integral.
\begin{example}[Harmonic Series]
    Given $\sum \frac{1}{n}$, we can use the integral test to show that the series diverges. We have:
        \int_1^{\infty} \frac{1}{x} \, dx &= \ln x \Big|_1^{\infty} \\
        &= \infty
    Thus, the series diverges. The harmonic series is a classic example of a divergent series.
\begin{definition}[Remainder]
    The remainder of a series $\sum a_n$ is given by:
        R_n = S - S_n = \sum_{k=n+1}^{\infty} a_k
    We can use the remainder to estimate the sum of a series.
\paragraph{Estimating Sums} We can estimate the sum of a series by using the remainder of the series. We can use the remainder to estimate the sum of a series. Note that we always have:
    R_n \le \int_n^{\infty} f(x) \, dx /quad \text{and} \quad R_n \ge \int_{n+1}^{\infty} f(x) \, dx
We can use it to estimate the sum of a series from a partial sum.
    S_n + \int_{n+1}^{\infty} f(x) \, dx \le S \le S_n + \int_n^{\infty} f(x) \, dx
    Given $\sum \frac{1}{n^2}$, we can use the remainder to estimate the sum of the series. We have:
        S_n + \int_{n+1}^{\infty} \frac{1}{x^2} \, dx &\le S \le S_n + \int_n^{\infty} \frac{1}{x^2} \, dx \\
        \frac{1}{n} + \int_{n+1}^{\infty} \frac{1}{x^2} \, dx &\le S \le \frac{1}{n} + \int_n^{\infty} \frac{1}{x^2} \, dx
    We can then evaluate the integrals to obtain the value bounds.
\subsection{Comparison Tests}
\begin{theorem}[Basic Comparison Test]
    Let $\{a_n\}$ and $\{b_n\}$ be two sequences such that $0 \le a_n \le b_n$ for all $n$. Then:
        \item If $\sum b_n$ converges, then $\sum a_n$ converges.
        \item If $\sum a_n$ diverges, then $\sum b_n$ diverges.
\begin{proof}
    Assume, WLOG, that $a_k \le b_k$ for all $k$. Define $S_n = \sum_{k=1}^{n} a_k$ and $T_n = \sum_{k=1}^{n} b_k$. Also, $T = \sum b_k$ exists. We have:
        S_{n+1} &= S_n + a_{n+1} > S_n
        \intertext{Thus, $\{S_n\}$ is increasing. Also, we have:}
        S_n &\le T_n < T
        \intertext{Thus, $\{S_n\}$ is bounded above. Thus, $\{S_n\}$ converges by the Monotone Convergence Theorem.}
\end{proof}
    Let $S = \sum \frac{7}{17n^2 + 3n^{1/3} + 5}$ We know that $17n^2 > 17n^{1/3} + 5$ for all $n$. Thus, we have:
        \frac{7}{17n^2} &> \frac{7}{17n^2 + 3n^{1/3} + 5} \\
        \intertext{We can then use the comparison test to show that the series converges.}

### 2025-02-06 MAT185 Lecture Notes/main.tex
feb 6

\documentclass[11pt]{article}
\input{preamble}
\begin{document}
\thispagestyle{empty}
{\LARGE \bf MAT 185 Lecture Notes}\\
{\large Hei Shing Cheung}\\
Linear Algebra, Winter 2024 \hfill MAT 185\\
\\
The up-to-date version of this document can be found at \url{https://github.com/HaysonC/skulenotes}\\
\section{Vector Space}
\subsection{Foundamental Properties}
\begin{definition}[Vector Space in $\mathbb{R}$]
    This course concerns with real vector spaces. A vectors space, ${V}$, over $\mathbb{R}$ is a collection of \textbf{object} $\textbf{v} \in V$ s.t. the follow axioms are followed
    \begin{enumerate}
        \item \textbf{Addition Axioms}
        \begin{enumerate}
            \item \textbf{Closure Under Addition:} \\
            $\textbf{x}, \textbf{y} \in V \implies \textbf{x} + \textbf{y} \in V$

@@

    \paragraph{Note} It could be shown that the axiom imply the commutativity of in addition, namely $\forall \textbf{x} \implies \textbf{y} \in \mathbb{R}$, $\textbf{x} + \textbf{y} = \textbf{y} + \textbf{x}$

@@

    Then, $\textbf{v}_1, \textbf{v}_2, \ldots, \textbf{v}_n$ are said to be linearly independent; otherwise, they are linearly dependent.
\end{definition}
\begin{definition}[Span]
    Let $V$ be a vector space and $\textbf{v}_1, \textbf{v}_2, \ldots, \textbf{v}_n \in V$, then:
    \begin{align}
        \text{Span}(\textbf{v}_1, \textbf{v}_2, \ldots, \textbf{v}_n) = \left\{ \alpha_1 \textbf{v}_1 + \alpha_2 \textbf{v}_2 + \ldots + \alpha_n \textbf{v}_n \, | \, \alpha_1, \alpha_2, \ldots, \alpha_n \in \mathbb{R} \right\}
    \end{align}
    is the set of all linear combinations of $\textbf{v}_1, \textbf{v}_2, \ldots, \textbf{v}_n$
\end{definition}
\begin{theorem}[Unique Representation]
    Let $V$ be a vector space and $\textbf{v}_1, \textbf{v}_2, \ldots, \textbf{v}_n \in V$ and $\alpha_1, \alpha_2, \ldots, \alpha_n \in \mathbb{R}/0$, and that they span $V$. For any $\textbf{v}_{n+1} \in V$, if $\textbf{v}_1, \textbf{v}_2, \ldots, \textbf{v}_n$ are linearly independent, then the equation:
    \begin{align*}
        \alpha_1 \textbf{v}_1 + \alpha_2 \textbf{v}_2 + \ldots + \alpha_n \textbf{v}_n = \textbf{v}_{n+1}  
    \end{align*} 
    is the only way to express $\textbf{v}_{n+1}$ as a linear combination of $\textbf{v}_1, \textbf{v}_2, \ldots, \textbf{v}_n$.
\end{theorem}
We can prove by contrapositive:
\begin{proof}
    Assume that there exists another way to express $\textbf{v}_{n+1}$ as a linear combination of $\textbf{v}_1, \textbf{v}_2, \ldots, \textbf{v}_n$, then:
    \begin{align*}
        \alpha_1 \textbf{v}_1 + \alpha_2 \textbf{v}_2 + \ldots + \alpha_n \textbf{v}_n = \beta_1 \textbf{v}_1 + \beta_2 \textbf{v}_2 + \ldots + \beta_n \textbf{v}_n
    \end{align*}
    Rearranging the equation, we have:
    \begin{align*}
        (\alpha_1 - \beta_1) \textbf{v}_1 + (\alpha_2 - \beta_2) \textbf{v}_2 + \ldots + (\alpha_n - \beta_n) \textbf{v}_n = \textbf{0}
    \end{align*}
    Since ($\alpha_i - \beta_i$) for $i = 1, 2, \ldots, n$ are not all zero, then $\textbf{v}_1, \textbf{v}_2, \ldots, \textbf{v}_n$ are linearly dependent. Thus, the contrapositive is true.
\end{proof}
\begin{theorem}[Growing and Pruning] The following are the two theorems describe the relationship between linear independence and the span: \\ \\
    \textbf{Growing} Let $V$ be a vector space and $\textbf{v}_1, \textbf{v}_2, \ldots, \textbf{v}_n \in V$ be linearly independent. If $\textbf{v}_{n+1} \in V$ and $\textbf{v}_{n+1} \notin \text{Span}(\textbf{v}_1, \textbf{v}_2, \ldots, \textbf{v}_n)$, then $\textbf{v}_1, \textbf{v}_2, \ldots, \textbf{v}_n, \textbf{v}_{n+1}$ are linearly independent. \\ \\
    \textbf{Pruning} Let $V$ be a vector space and $\textbf{v}_1, \textbf{v}_2, \ldots, \textbf{v}_n \in V$. If $\textbf{v}_1, \textbf{v}_2, \ldots, \textbf{v}_n$ are linearly dependent, then there exists a $\textbf{v}_i$ such that $\textbf{v}_i \in \text{Span}(\textbf{v}_1, \textbf{v}_2, \ldots, \textbf{v}_{i-1}, \textbf{v}_{i+1}, \ldots, \textbf{v}_n)$.
\end{theorem}
\begin{definition}[Basis]
    Let $V$ be a vector space and $\textbf{v}_1, \textbf{v}_2, \ldots, \textbf{v}_n \in V$. If $\textbf{v}_1, \textbf{v}_2, \ldots, \textbf{v}_n$ are linearly independent and $\text{Span}(\textbf{v}_1, \textbf{v}_2, \ldots, \textbf{v}_n) = V$, then $\textbf{v}_1, \textbf{v}_2, \ldots, \textbf{v}_n$ is a basis of $V$.
\end{definition}
\subsection{Fundamental Theorem of Linear Algebra}
\begin{theorem}[Fundamental Theorem of Linear Algebra]
    Let $V$ be a vector space and $\textbf{v}_1, \textbf{v}_2, \ldots, \textbf{v}_n \in V$. If $\textbf{v}_1, \textbf{v}_2, \ldots, \textbf{v}_n$ are linearly independent and $\text{Span}(\textbf{v}_1, \textbf{v}_2, \ldots, \textbf{v}_n) = V$, then:
    \begin{enumerate}
        \item Any basis of $V$ has the same number of elements.
        \item Any linearly independent set of $V$ has at most $n$ elements.
        \item Any spanning set of $V$ has at least $n$ elements.
    \end{enumerate}
\end{theorem}
\end{document}

>>>>

\documentclass[11pt]{article}
\input{preamble}
\begin{document}
\thispagestyle{empty}
{\LARGE \bf MAT 185 Lecture Notes}\\
{\large Hei Shing Cheung}\\
Linear Algebra, Winter 2024 \hfill MAT 185\\
\\
The up-to-date version of this document can be found at \url{https://github.com/HaysonC/skulenotes}\\
\section{Vector Space}
\subsection{Foundamental Properties}
\begin{definition}[Vector Space in $\mathbb{R}$, Field]
    This course concerns with real vector spaces. A vectors space, ${V}$, over $\mathbb{R}$ is a collection of \textbf{object} $\textbf{v} \in V$ s.t. the follow axioms are followed
    \begin{enumerate}
        \item \textbf{Addition Axioms}
        \begin{enumerate}
            \item \textbf{Closure Under Addition:} \\
            $\textbf{x}, \textbf{y} \in V \implies \textbf{x} + \textbf{y} \in V$

@@

    \paragraph{Note} It could be shown that the axiom imply the commutativity of in addition, namely $\forall \textbf{x}, \textbf{y} \in \mathbb{R}$, $\textbf{x} + \textbf{y} = \textbf{y} + \textbf{x}$

@@

    Then, $\textbf{v}_1, \textbf{v}_2, \ldots, \textbf{v}_n$ are said to be linearly independent; otherwise, they are linearly dependent.
\begin{definition}[Span]
    Let $V$ be a vector space and $\textbf{v}_1, \textbf{v}_2, \ldots, \textbf{v}_n \in V$, then:
        \text{Span}(\textbf{v}_1, \textbf{v}_2, \ldots, \textbf{v}_n) = \left\{ \alpha_1 \textbf{v}_1 + \alpha_2 \textbf{v}_2 + \ldots + \alpha_n \textbf{v}_n \, | \, \alpha_1, \alpha_2, \ldots, \alpha_n \in \mathbb{R} \right\}
    is the set of all linear combinations of $\textbf{v}_1, \textbf{v}_2, \ldots, \textbf{v}_n$
\begin{theorem}[Unique Representation]
    Let $V$ be a vector space and $\textbf{v}_1, \textbf{v}_2, \ldots, \textbf{v}_n \in V$ and $\alpha_1, \alpha_2, \ldots, \alpha_n \in \mathbb{R}/0$, and that they span $V$. For any $\textbf{v}_{n+1} \in V$, if $\textbf{v}_1, \textbf{v}_2, \ldots, \textbf{v}_n$ are linearly independent, then the equation:
        \alpha_1 \textbf{v}_1 + \alpha_2 \textbf{v}_2 + \ldots + \alpha_n \textbf{v}_n = \textbf{v}_{n+1}  
    is the only way to express $\textbf{v}_{n+1}$ as a linear combination of $\textbf{v}_1, \textbf{v}_2, \ldots, \textbf{v}_n$.
We can prove by contrapositive:
    Assume that there exists another way to express $\textbf{v}_{n+1}$ as a linear combination of $\textbf{v}_1, \textbf{v}_2, \ldots, \textbf{v}_n$, then:
        \alpha_1 \textbf{v}_1 + \alpha_2 \textbf{v}_2 + \ldots + \alpha_n \textbf{v}_n = \beta_1 \textbf{v}_1 + \beta_2 \textbf{v}_2 + \ldots + \beta_n \textbf{v}_n
    Rearranging the equation, we have:
        (\alpha_1 - \beta_1) \textbf{v}_1 + (\alpha_2 - \beta_2) \textbf{v}_2 + \ldots + (\alpha_n - \beta_n) \textbf{v}_n = \textbf{0}
    Since ($\alpha_i - \beta_i$) for $i = 1, 2, \ldots, n$ are not all zero, then $\textbf{v}_1, \textbf{v}_2, \ldots, \textbf{v}_n$ are linearly dependent. Thus, the contrapositive is true.
\begin{theorem}[Growing and Pruning] The following are the two theorems describe the relationship between linear independence and the span: \\ \\
    \textbf{Growing} Let $V$ be a vector space and $\textbf{v}_1, \textbf{v}_2, \ldots, \textbf{v}_n \in V$ be linearly independent. If $\textbf{v}_{n+1} \in V$ and $\textbf{v}_{n+1} \notin \text{Span}(\textbf{v}_1, \textbf{v}_2, \ldots, \textbf{v}_n)$, then $\textbf{v}_1, \textbf{v}_2, \ldots, \textbf{v}_n, \textbf{v}_{n+1}$ are linearly independent. \\ \\
    \textbf{Pruning} Let $V$ be a vector space and $\textbf{v}_1, \textbf{v}_2, \ldots, \textbf{v}_n \in V$. If $\textbf{v}_1, \textbf{v}_2, \ldots, \textbf{v}_n$ are linearly dependent, then there exists a $\textbf{v}_i$ such that $\textbf{v}_i \in \text{Span}(\textbf{v}_1, \textbf{v}_2, \ldots, \textbf{v}_{i-1}, \textbf{v}_{i+1}, \ldots, \textbf{v}_n)$.
\begin{theorem}[Span and Linear Independence]
    Let $V$ be a vector space and $\textbf{v}_1, \textbf{v}_2, \ldots, \textbf{v}_n \in V$. For every $\textbf{v}_k$ with $k = 1, 2, \ldots, n$, $\text{Span}(\textbf{v}_1, \textbf{v}_2, \ldots, \textbf{v}_{k-1}, \textbf{v}_{k+1}, \ldots, \textbf{v}_n) \subset \text{Span}(\textbf{v}_1, \ldots, \textbf{v}_n)$ if and only if $\textbf{v}_1, \textbf{v}_2, \ldots, \textbf{v}_n$ are linearly independent.
\begin{definition}[Basis]
    Let $V$ be a vector space and $\textbf{v}_1, \textbf{v}_2, \ldots, \textbf{v}_n \in V$. If $\textbf{v}_1, \textbf{v}_2, \ldots, \textbf{v}_n$ are linearly independent and $\text{Span}(\textbf{v}_1, \textbf{v}_2, \ldots, \textbf{v}_n) = V$, then $\textbf{v}_1, \textbf{v}_2, \ldots, \textbf{v}_n$ is a basis of $V$.
\subsection{Fundamental Theorem of Linear Algebra}
\begin{theorem}[Fundamental Theorem of Linear Algebra]
    Let $V$ be a vector space and $\textbf{v}_1, \textbf{v}_2, \ldots, \textbf{v}_n \in V$. If $\textbf{v}_1, \textbf{v}_2, \ldots, \textbf{v}_n$ are linearly independent and $\text{Span}(\textbf{v}_1, \textbf{v}_2, \ldots, \textbf{v}_n) = V$, then:
        \item Any basis of $V$ has the same number of elements.
        \item Any linearly independent set of $V$ has at most $n$ elements.
        \item Any spanning set of $V$ has at least $n$ elements.
\begin{example}[Dimension of Even 4-degree polynomial]
    Given $W \subseteq \mathbb{P}_4$ where $W = \left\{ p(x) \, | \, p(x) = p(-x) \right\}$, then $W$ is a subspace of $\mathbb{P}_4$. Since $x^3, x \in P_4$ but $x^3, x \notin W$,  Span$(\{W, x, x^3\}) = \mathrm{dim}(W) + 2$ So $\mathrm{dim}(W) \le 3$; We can find 3 linearly independent vectors in $W$ such as $1, x^2, x^4$. Thus, $\mathrm{dim}(W) \ge 3$. Thus, $\mathrm{dim}(W) = 3$.
\end{example}

\begin{definition}[Column Space]
    Let $a_1, a_2, \ldots, {a_n} \in {^m\mathbb{R}}$, then:   
    \begin{equation}
        \text{Col}(A) = \text{Span}({a_1}, {a_2}, \ldots, {a_n})
    \end{equation}
    is the column space of $A$.
\end{definition}
Note that the span of set is a subspace of the vector space. Thus, the column space of a matrix is a subspace of $^m\mathbb{R}$. This is also call the set of images of the transformation. We can also note that matrix multiplication is is commutative with scalar multiplication. We can conduct proofs using such properties.
\begin{definition}[Rank]
    Let $A \in {^m\mathbb{R}^n}$, then:
    \begin{equation}
        \text{rank}(A) = \text{dim}(\text{Col}(A))
    \end{equation}
    is the rank of $A$.
\end{definition}
\end{document}

### 2025-02-06 MSE160 Lecture Notes/main.tex
feb 6

\includepdf[pages=-, angle=90]{EquationSheet.pdf}
\end{document}

>>>>

\subsection{Geometrcally Ideal Crystal Structures}
\paragraph{Coordination Number and Ratio} The coordination number increases with $\frac{r_{\text{cation}}}{r_{\text{anion}}}$ (The ionic radii ratio).  It relates to coordination number as follows:
\begin{table}[h]
    \centering
    \begin{tabular}{|c|c|c|}
        \hline
        \textbf{Ionic Radii Ratio} & \textbf{Coord. Number} & \textbf{Name} \\
        \hline
        $<$ 0.155 & 2 & Linear \\
        0.155 - 0.225 & 3 & Trigonal Planar \\
        0.225 - 0.414 & 4 & Tetrahedral \\
        0.414 - 0.732 & 6 & Octahedral \\
        0.732 - 1.0 & 8 & Cubic \\
        \hline
    \end{tabular}
    \caption{Coordination Number and Ionic Radii}
    \label{tab:coordination-number}
\end{table} 
\begin{definition}[AX Type]
    The AX type is a crystal structure where the cation and anion are of the same ratio. 
\begin{example}[AX Type: $\ch{NaCl}$ rock salt]
    The $\ch{NaCl}$ structure is an AX type structure. The cation and anion are of the same ratio. Soldium (Cation) has radius $r_{\text{Na}} = 0.102$ nm and Chlorine (Anion) has radius $r_{\text{Cl}} = 0.181$ nm. The ratio is:
    $$ \frac{r_{\text{cation}}}{r_{\text{anion}}} = \frac{0.102}{0.181} = 0.56 $$
    Thus, the coordination number is 6.\\
    Additionally, we could calculate its theoretical density. It has 4 cation and 4 anion in the unit cell. The volume of the unit cell is $a^3$, and it follows a FCC structure. Thus, the density is: 
        \rho &= \frac{4M_{\text{Na}} + 4M_{\text{Cl}}}{a^3 N_A} = \frac{4(22.99) + 4(35.45)}{a^3 N_A} \\
        &= \frac{4(22.99) + 4(35.45)}{(2\sqrt{2}r_{\text{Na}})^3 N_A} = \frac{4(22.99) + 4(35.45)}{(2\sqrt{2} \times 0.102)^3 N_A} \\
        &= \frac{4(22.99) + 4(35.45)}{(2\sqrt{2} \times 0.102)^3 N_A} = 2.16 \text{ g/cm}^3
\begin{example}[AX Type: $\ch{ZnS}$, Zinc Blende]
    The $\ch{ZnS}$ structure is an AX type structure. It has a FCC structure with CN = 4. The radius of Zinc (Cation) is $r_{\text{Zn}} = 0.074$ nm and the radius of Sulfur (Anion) is $r_{\text{S}} = 0.184$ nm. The ratio is:
    $$ \frac{r_{\text{cation}}}{r_{\text{anion}}} = \frac{0.074}{0.184} = 0.40 $$
\begin{example}[AX$_2$ Type: $\ch{CaF2}$]
    The $\ch{CaF2}$ structure is an AX$_2$ type structure. It has a FCC structure with CN = 8. The radius of Calcium (Cation) is $r_{\text{Ca}} = 0.099$ nm and the radius of Fluorine (Anion) is $r_{\text{F}} = 0.133$ nm. The ratio is:
    $$ \frac{r_{\text{cation}}}{r_{\text{anion}}} = \frac{0.099}{0.133} = 0.74 $$
\includepdf[pages=-, angle=90]{EquationSheet.pdf}
\end{document}
